An indexed construction of semi-simplicial and semi-cubical types

### 2022-05-18 paper/paper.tex
paper: get prepared to pass explicit arguments to xkeyval

% Frame, layer, and filler: the general macro
\newcommandx{\prim}[5][2=,3=,4=,5=]{\ensuremath{\mathsf{\color{indian-yellow}{#1}}_{#2}^{\joinargs{}[#3][#4][#5]}}}

% Restriction for frame, layer, and filler: the general macro
\newcommandx{\restr}[7][2=,3=,4=,5=,6=,7=]{\ensuremath{\mathsf{\color{russian-green}{restr}}_{\mathsf{\color{indian-yellow}{#1}}\joinargs{,}[#2][#3][#4]}^{\joinargs{}[#5][#6][#7]}}}

% Coherence conditions for frame, layer, and filler: the general macro
\newcommandx{\coh}[9][2=,3=,4=,5=,6=,7=,8=,9=]{\ensuremath{\mathsf{\color{chestnut}{coh}}_{\mathsf{\color{indian-yellow}{#1}}\joinargs{,}[#2][#3][#4][#5][#6]}^{\joinargs{}[#7][#8][#9]}}}

@@

% Frame, layer, and filler
% Drop the universe letter
\newcommandx{\framep}[4][1=,2=,3=,4=]{\prim{frame}[][#2][#3][#4]}
\newcommandx{\layer}[4][1=,2=,3=,4=]{\prim{layer}[][#2][#3][#4]}
\newcommandx{\filler}[4][1=,2=,3=,4=]{\prim{filler}[][#2][#3][#4]}

% Restriction for frame, layer, and filler
% Drop the unviverse letter and q
\newcommandx{\restrf}[6][1=,2=,3=,4=,5=,6=]{\restr{frame}[][#2][][#4][#5][#6]}
\newcommandx{\restrl}[6][1=,2=,3=,4=,5=,6=]{\restr{layer}[][#2][][#4][#5][#6]}
\newcommandx{\restrc}[6][1=,2=,3=,4=,5=,6=]{\restr{filler}[][#2][][#4][#5][#6]}

% Coherence conditions for frame, layer, and filler
% Keep only ε, ω; n, p; proposition on n and p
\newcommandx{\cohf}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{frame}[][#2][#3][][][#6][#7][#8]}
\newcommandx{\cohl}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{layer}[][#2][#3][][][#6][#7][#8]}
\newcommandx{\cohc}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{filler}[][#2][#3][][][#6][#7][#8]}

@@

% Truncated sets, otherwise referred to as X
% Drop the universe letter for the third and fourth tables
\renewcommandx{\Xto}[2]{\X[][<#2]}
\renewcommandx{\Xcomp}[2]{\X[][=#2]}
\renewcommandx{\Xfrom}[2]{\X[][\geq#2]}
\input{tab-faces.tex}

% Restriction for frame, layer, and filler
% Drop just the universe letter for the coh table
\renewcommandx{\restrf}[6][1=,2=,3=,4=,5=,6=]{\restr{frame}[][#2][#3][#4][#5][#6]}
\renewcommandx{\restrl}[6][1=,2=,3=,4=,5=,6=]{\restr{layer}[][#2][#3][#4][#5][#6]}
\renewcommandx{\restrc}[6][1=,2=,3=,4=,5=,6=]{\restr{filler}[][#2][#3][#4][#5][#6]}

% Frame, layer, and filler
% Drop all arguments for coh table; they're not present in coind table.
\renewcommandx{\framep}[4][1=,2=,3=,4=]{\prim{frame}[][][][]}
\renewcommandx{\layer}[4][1=,2=,3=,4=]{\prim{layer}[][][][]}
\renewcommandx{\filler}[4][1=,2=,3=,4=]{\prim{filler}[][][][]}

% Coherence conditions for frame, layer, and filler
% Drop universe letter, ε, and ω
\renewcommandx{\cohf}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{frame}[][][][#4][#5][#6][#7][#8]}
\renewcommandx{\cohl}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{layer}[][][][#4][#5][#6][#7][#8]}
\renewcommandx{\cohc}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{filler}[][][][#4][#5][#6][#7][#8]}
\input{tab-coh.tex}

@@

\newpage
\appendix
\section{Tables in full detail}
% Keep all arguments for all macros
% Frame, layer, and filler
\renewcommandx{\framep}[4][1=,2=,3=,4=]{\prim{frame}[#1][#2][#3][#4]}
\renewcommandx{\layer}[4][1=,2=,3=,4=]{\prim{layer}[#1][#2][#3][#4]}
\renewcommandx{\filler}[4][1=,2=,3=,4=]{\prim{filler}[#1][#2][#3][#4]}
\renewcommandx{\fullframe}[2][1=,2=]{\prim{fullframe}[#1][#2][][]}

% Restriction for frame, layer, and filler
\renewcommandx{\restrf}[6][1=,2=,3=,4=,5=,6=]{\restr{frame}[#1][#2][#3][#4][#5][#6]}
\renewcommandx{\restrl}[6][1=,2=,3=,4=,5=,6=]{\restr{layer}[#1][#2][#3][#4][#5][#6]}
\renewcommandx{\restrc}[6][1=,2=,3=,4=,5=,6=]{\restr{filler}[#1][#2][#3][#4][#5][#6]}

% Coherence conditions for frame, layer, and filler
\renewcommandx{\cohf}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{cohframe}[#1][#2][#3][#4][#5][#6][#7][#8]}
\renewcommandx{\cohl}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{cohlayer}[#1][#2][#3][#4][#5][#6][#7][#8]}
\renewcommandx{\cohc}[8][1=,2=,3=,4=,5=,6=,7=,8=]{\coh{cohfiller}[#1][#2][#3][#4][#5][#6][#7][#8]}

>>>>

% Magic with xkeyval to go over the 9-argument limit of LaTeX
\makeatletter
\define@key{Ex}{D}{#1}
\define@key{Ex}{d}{#1}
\define@key{Ex}{E}{#1}
\define@key{Ex}{l}{#1}
\define@key{Ex}{c}{#1}
\makeatother

% Frame, layer, and filler: the general macro
\makeatletter
\newcommandx{\prim}[6][2=,3=,4=,5=,6=]{\ensuremath{\mathsf{\color{indian-yellow}{#1}}_{#2}^{\joinargs{}[#3][#4][#5]}\@ifstar{}{\setkeys*{Ex}{#6}}}}
\makeatother

% Restriction for frame, layer, and filler: the general macro
\makeatletter
\newcommandx{\restr}[8][2=,3=,4=,5=,6=,7=,8=]{\ensuremath{\mathsf{\color{russian-green}{restr}}_{\mathsf{\color{indian-yellow}{#1}}\joinargs{,}[#2][#3][#4]}^{\joinargs{}[#5][#6][#7]}\@ifstar{}{\setkeys*{Ex}{#8}}}}
\makeatother

% Coherence conditions for frame, layer, and filler: the general macro

% Hack: we'd like \coh to take 10 arguments, with the 10th being passed to
% xkeyval, but this is not possible. The only possible compromise is to join
% #7, and #8 by hand in usage of \coh, by hand.
\makeatletter
\newcommandx{\coh}[9][2=,3=,4=,5=,6=,7=,8=,9=]{\ensuremath{\mathsf{\color{chestnut}{coh}}_{\mathsf{\color{indian-yellow}{#1}}\joinargs{,}[#2][#3][#4][#5][#6]}^{\joinargs{}[#7][#8]}\@ifstar{}{\setkeys*{Ex}{#9}}}}
\makeatother

@@

% Frame, layer, and filler
% Drop the universe letter
\newcommandx{\framep}[5][1=,2=,3=,4=,5=]{\prim{frame}[][#2][#3][#4][#5]}
\newcommandx{\layer}[5][1=,2=,3=,4=,5=]{\prim{layer}[][#2][#3][#4][#5]}
\newcommandx{\filler}[5][1=,2=,3=,4=,5=]{\prim{filler}[][#2][#3][#4][#5]}

% Restriction for frame, layer, and filler
% Drop the unviverse letter and q
\newcommandx{\restrf}[7][1=,2=,3=,4=,5=,6=,7=]{\restr{frame}[][#2][][#4][#5][#6][#7]}
\newcommandx{\restrl}[7][1=,2=,3=,4=,5=,6=,7=]{\restr{layer}[][#2][][#4][#5][#6][#7]}
\newcommandx{\restrc}[7][1=,2=,3=,4=,5=,6=,7=]{\restr{filler}[][#2][][#4][#5][#6][#7]}

% Coherence conditions for frame, layer, and filler
% Keep only ε, ω; n, p; proposition on n and p
\newcommandx{\cohf}[9][1=,2=,3=,4=,5=,6=,7=,8=,9=]{\coh{frame}[][#2][#3][][][][][#9]}
\newcommandx{\cohl}[9][1=,2=,3=,4=,5=,6=,7=,8=,9=]{\coh{layer}[][#2][#3][][][][][#9]}
\newcommandx{\cohc}[9][1=,2=,3=,4=,5=,6=,7=,8=,9=]{\coh{filler}[][#2][#3][][][][][#9]}

@@

% Truncated sets, otherwise referred to as X
% Drop the universe letter for the third and fourth tables
\renewcommandx{\Xto}[2]{\X[][<#2]}
\renewcommandx{\Xcomp}[2]{\X[][=#2]}
\renewcommandx{\Xfrom}[2]{\X[][\geq#2]}

% The third table mentions cohframe; keep ε, ω in this instance
\renewcommandx{\cohf}[9][1=,2=,3=,4=,5=,6=,7=,8=,9=]{\coh{frame}[][#2][#3][][][#6,#7][#8][#9]}
\input{tab-faces.tex}

% Restriction for frame, layer, and filler
% Drop just the universe letter for the coh table
\renewcommandx{\restrf}[7][1=,2=,3=,4=,5=,6=,7=]{\restr{frame}[][#2][#3][#4][#5][#6][#7]}
\renewcommandx{\restrl}[7][1=,2=,3=,4=,5=,6=,7=]{\restr{layer}[][#2][#3][#4][#5][#6][#7]}
\renewcommandx{\restrc}[7][1=,2=,3=,4=,5=,6=,7=]{\restr{filler}[][#2][#3][#4][#5][#6][#7]}

% Frame, layer, and filler
% Drop all arguments for coh table; they're not present in coind table.
\renewcommandx{\framep}[5][1=,2=,3=,4=,5=]{\prim{frame}[][][][][]}
\renewcommandx{\layer}[5][1=,2=,3=,4=,5=]{\prim{layer}[][][][][]}
\renewcommandx{\filler}[5][1=,2=,3=,4=,5=]{\prim{filler}[][][][][]}

% Coherence conditions for frame, layer, and filler
% Drop universe letter, ε, and ω
\renewcommandx{\cohf}[9][1=,2=,3=,4=,5=,6=,7=,8=,9=]{\coh{frame}[][][][#4][#5][#6,#7][#8][#9]}
\renewcommandx{\cohl}[9][1=,2=,3=,4=,5=,6=,7=,8=,9=]{\coh{layer}[][][][#4][#5][#6,#7][#8][#9]}
\renewcommandx{\cohc}[9][1=,2=,3=,4=,5=,6=,7=,8=,9=]{\coh{filler}[][][][#4][#5][#6,#7][#8][#9]}
\input{tab-coh.tex}

@@

\newpage
\appendix
\section{Tables in full detail}
% Keep all arguments for all macros
% Frame, layer, and filler
\renewcommandx{\framep}[5][1=,2=,3=,4=,5=]{\prim{frame}[#1][#2][#3][#4][#5]}
\renewcommandx{\layer}[5][1=,2=,3=,4=,5=]{\prim{layer}[#1][#2][#3][#4][#5]}
\renewcommandx{\filler}[5][1=,2=,3=,4=,5=]{\prim{filler}[#1][#2][#3][#4][#5]}
\renewcommandx{\fullframe}[2][1=,2=]{\prim{fullframe}[#1][#2][][]}

% Restriction for frame, layer, and filler
\renewcommandx{\restrf}[7][1=,2=,3=,4=,5=,6=,7=]{\restr{frame}[#1][#2][#3][#4][#5][#6][#7]}
\renewcommandx{\restrl}[7][1=,2=,3=,4=,5=,6=,7=]{\restr{layer}[#1][#2][#3][#4][#5][#6][#7]}
\renewcommandx{\restrc}[7][1=,2=,3=,4=,5=,6=,7=]{\restr{filler}[#1][#2][#3][#4][#5][#6][#7]}

% Coherence conditions for frame, layer, and filler
\renewcommandx{\cohf}[9][1=,2=,3=,4=,5=,6=,7=,8=,9=]{\coh{cohframe}[#1][#2][#3][#4][#5][#6,#7][#8][#9]}
\renewcommandx{\cohl}[9][1=,2=,3=,4=,5=,6=,7=,8=,9=]{\coh{cohlayer}[#1][#2][#3][#4][#5][#6,#7][#8][#9]}
\renewcommandx{\cohc}[9][1=,2=,3=,4=,5=,6=,7=,8=,9=]{\coh{cohfiller}[#1][#2][#3][#4][#5][#6,#7][#8][#9]}
